---
title: "Explanation of UNZCubeDataTools package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
What follows is a list and description of each component folder and file contained within the package repository.
```{r setup}
library(UNZCubeDataTools)
```


### *Data source for entire tool*: datacube.RData 
Contains datacube.v2, the summary data by group being fed into the graphs for this tool

### man 
Documentation (currently for a single function)

### DESCRIPTION 
Package metadata

### cubehelpers.RData 
Contains a table of descriptions of the variables (e.g., what it means for an individual to be ‘Overseas’)

### shinyappload.R 
Runs the following codes, all contained within the folder R:

#### a.	option setup.R 
Creates lists of codings for each possible value of each variable. E.g. for youngGradOptions, Combined = -1, Young Graduate = 1, and Mature Graduate = 0

#### b.	data setup.R 
Does some tidying and descriptions around variable names

#### c.	cube data functions.R
First creates a series of functions (getCube….select()), two for domestic students and two for international students, that take an indicator.data and optionSet argument and return a logical value. It checks whether the selected variable option (sex, ethnicity, etc.) is in the selected dataset.

### Tests	
Performs tests to ensure functions work as expected


## Additional notes

### Explanation of variable optionSet
A common variable that is passed to functions is `optionSet`. The meaning of this is as follows:  

A list/vector with the following fields: list(dom = bool, sex = int, eth = int, studyLevel = int, subsector = string, fieldOfStudy = int, cohort = int, indicator = string).

### Cube Data Functions process:
NB:   
International students only have field and level of study data available. We need to deal with these
two groups differently.  
For domestic students where income data is available, we deal with it differently from other data. Income data has means and medians available, whereas other data such as number overseas is a simple division of numerator (number of students overseas) divided by denominator (total number of students).   

The first two steps involved in this R script are as follows. See code itself for additional comments.

1. Create list of Full and Code names for variables in data setup.R
2. Create function which assigns a function to optionSet depending on whether any cohorts are missing 
and whether we are looking at international students or not.

