---
title: "Explanation of UNZCubeDataTools package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(UNZCubeDataTools)
```

### man 
Documentation (currently for a single function)

### DESCRIPTION 
Package metadata

### cubehelpers.RData 
Contains a table of descriptions of the variables (e.g., what it means for an individual to be ‘Overseas’)

### datacube.RData 
Contains datacube.v2, the summary data by group being fed into the graphs for this tool

### shinyappload.R 
Runs the following codes, all contained within the folder R:

#### a.	option setup.R 
Creates lists of codings for each possible value of each variable. E.g. for youngGradOptions, Combined = -1, Young Graduate = 1, and Mature Graduate = 0

#### b.	data setup.R 
Does some tidying and descriptions around variable names

#### c.	cube data functions.R
First creates a series of functions (getCube….select()), two for domestic students and two for international students, that take an indicator.data and optionSet argument and return a logical value. It checks whether the selected variable option (sex, ethnicity, etc.) is in the selected dataset.

### 6.	
Tests performs tests to ensure functions work as expected
